---
title: "Google API"
author: "Zhendong Wang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Examples

The `google_api` function is used to create an object in class `google_api_class`, which owns four attributes: content, address, query, response. 

```{r, fig.show='hold'}
library(httr)
library(jsonlite)
example <-Lab5::google_api("Eiffel+Tower,Paris")
example$address
example$url

```

Also, you could use `google_api()` function to print all the information it contains.
```{r}
Lab5::google_api("Summer+Palace,Beijing")

```



> "Google_API."([source](https://developers.google.com/maps/documentation/geocoding/intro))
